\section{experience}
\resumeSubHeadingListStart

\resumeSubheadingWork
{\href{https://www.kadam.net/}{Kadam}}{Limassol, Cyprus}
{MLOps Engineer}{May 2023 - Present}
{Department: Data Science and Analytics}{Remote}
\resumeItemListStart
\resumeItem{Redesign projects for CTR prediction and anti-fraud systems. Developed alerting system.}
\resumeItem{Integrated CI/CD, Docker, A/B-testing, Prefect, Airflow, unit-tests, linters, code-review.}
\resumeItemListEnd

\resumeSubheadingWork
{\href{https://www.karpov.courses/}{Karpov.Courses}}{Moscow, Russia}
{Head of Experts $|$ Content Creator}{April 2022 - Present}
{Courses: Start ML $|$ DL Engineer $|$ Hard ML $|$ Data Engineer $|$ Simulator A/B-testing}{Remote}
\resumeItemListStart
\resumeItem{30 streams of students graduated. Lead a team of 8 ML experts. Trained 10 interns.}
\resumeItem{Designed MLOps and Dynamic Pricing modules at HardML course.}
\resumeItemListEnd

\resumeSubheadingWork
{\href{https://siberianhealth.com/en}{Siberian Wellness}}{Novosibirsk, Russia}
{Data Scientist}{January 2022 - December 2022}
{Department: Data Analysis}{Remote}
\resumeItemListStart
\resumeItem{Design analytical reports with anomaly detection. Improve Data-Driven Decision Making.}
\resumeItem{Developed numerous ETL/ML pipelines for dashboards and auto-reports.}
\resumeItemListEnd

\resumeSubheadingWork
{\href{https://www.chmtch.com/}{ChemTech AI}}{New-York, USA}
{Data Scientist}{October 2020 - December 2021}
{Team: Data Science}{Remote}
\resumeItemListStart
\resumeItem{Refactoring 3 legacy prediction projects from TensorFlow to LGBM/CatBoost.}
\resumeItem{Developed computer-vision systems for object detection and OCR.}
\resumeItemListEnd

\resumeSubHeadingListEnd
